Hybrid MILP to efficiently and accuratly \\ solve hard DNN verification instances

### 2024-11-26 ICLR25/introduction.tex
intro

	\item {\color{blue} We designed a novel Utility function to choose few neurons to encode with the exact MILP encoding, while others are treated with the efficient LP relaxation, giving rise to partial MILP (pMILP). Specifically, the novelty of Utility resides in the use of the solution to an (efficient LP) solver on the node $z$ we want to bound. Utility can then precisely evaluate how much accuracy is gained by switching neuron $a$ from LP (solution of the LP call) to the exact MILP encoding of ReLU (exact computation from the solution, which can be made thanks to Proposition \ref{LP}), with a proved bound on the precision (Proposition \ref{prop2}). pMILP is much more efficient than previous attempts \cite{DivideAndSlide}, necessitating $\approx 4$ times less integer variables for the same accuracy 
	(Table \ref{tab:example1}), because Utility focuses on the solution local to the input, rather than on the DNN. To the best of our knowledge, this is the first time such a solution of an (LP) call is used to evaluate the contribution of each neuron, including heuristics for BaB, e.g. \cite{ferrari2022complete,crown}.}

>>>>

	\item {\color{blue} We designed a novel Utility function to choose few neurons to encode with the exact MILP encoding, while others are treated with the efficient LP relaxation, giving rise to partial MILP (pMILP). Specifically, the novelty of Utility resides in the use of the solution to an (efficient LP) solver on the node $z$ we want to bound. Utility can then precisely evaluate how much accuracy is gained by switching neuron $a$ from LP (solution of the LP call) to the exact MILP encoding of ReLU (exact computation from the solution, which can be made thanks to Proposition \ref{LP}), with a proved bound on the precision (Proposition \ref{prop2}). Because pMILP focuses on the gain (binary - linear),
	it is much more efficient ($\approx 4$ times less integer variables for same accuracy (Table \ref{tab:example1})) than previous attempts, which consider the full contribution of a neuron. To the best of our knowledge, this is the first time such a solution of an (LP) call is used to evaluate the contribution of each neuron, including heuristics for BaB, e.g. \cite{ferrari2022complete,crown}.}
